%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Dylan M Taylor Resume
% February 3, 2020
%
% Heavily modified (naturally) from https://github.com/deedydas/Deedy-Resume by Debarghya Das (http://debarghyadas.com)
% Licensed under the Apache License 2.0.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{dylan-resume}
\author{Dylan M. Taylor}
\title{Dylan M. Taylor Résumé}
\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LAST UPDATED DATE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\lastupdated

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     TITLE NAME
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\vspace*{3em}
\namesection{Dylan M. Taylor}{
\urlstyle{same}\href{https://dylanmtaylor.com}{dylanmtaylor.com} |
\href{mailto:dylan@dylanmtaylor.com}{dylan@dylanmtaylor.com} |
\href{https://durhamnc.gov/}{Durham, North Carolina 27703}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     MAIN SECTION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\hfill
\begin{minipage}[t]{1.00\textwidth}
\vspace*{0.5em}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     PROFESSIONAL SUMMARY
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{PROFESSIONAL SUMMARY}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item {\textbf{Championing cloud-native development and infrastructure-as-code (IaC):}} Led the development of multiple CI/CD solutions, container images, customized \href{https://www.packer.io/}{Packer} images, and production-grade Terraform repositories/modules, ensuring standardized, scalable deployments within the company's cloud environments. Focused on reusability when developing modules so that the DRY principle could be applied, ensuring uniformity across many accounts and deployments.
\item {\textbf{Scripting and automation:}} Developed a Python-based \href{https://www.selenium.dev/}{Selenium} script for automated environment configuration and testing of a line-of-business application, streamlining deployment processes, reducing manual intervention and improving operational efficiency. Migrated complex business processes to cloud-native architecture on AWS, utilizing \href{https://aws.amazon.com/step-functions/}{Step Functions}, \href{https://aws.amazon.com/lambda/}{Lambda}, and \href{https://aws.amazon.com/batch/}{Batch}, for efficient job processing and reduced operational costs.
\item {\textbf{Enhancing cloud security posture:}} Developed an \href{https://www.ansible.com/}{Ansible} playbook and provisioning scripts to configure machines to follow corporate standards, ensuring auditability, separation of duties, and LDAP integration. Worked closely with cyber security to build out monitoring and auditing solutions using Security Lake and the \href{https://www.rapid7.com/products/insight-platform/}{Rapid7 Insight Platform} in an automated fashion. 
\item {\textbf{Linux administration:}} Seasoned Linux administrator both as a hobbyist and a professional, with extensive experience in system provisioning, configuration management, performance optimization, and troubleshooting across various distributions. Contributed to FOSS projects in spare time, providing code, automation, and packaging for components of \href{https://archlinux.org/}{Arch Linux} (writing \href{https://github.com/archlinux/archinstall/graphs/contributors}{Python code for the installer}), \href{https://nixos.org/}{NixOS} (as a package maintainer), and GitHub Actions for the \href{https://universal-blue.org/}{Universal Blue images}.
\item {\textbf{Cloud networking:}} Helped to design and implement robust and secure multi-regional cloud network infrastructure using \href{https://aws.amazon.com/vpc/}{VPC}, \href{https://aws.amazon.com/cloudwan/}{CloudWAN}, \href{https://aws.amazon.com/network-firewall/}{AWS network firewall}, \href{https://docs.aws.amazon.com/AWSEC2/latest/UserGuide/ec2-security-groups.html}{network security group rules}, \href{https://aws.amazon.com/route53/}{Route53}, and Elastic Load Balancers (both \href{https://aws.amazon.com/elasticloadbalancing/application-load-balancer/}{ALB} and \href{https://aws.amazon.com/elasticloadbalancing/network-load-balancer/}{NLB}). Centralized network routing and configuration for several dozen accounts for enhanced security and manageability.
\item {\textbf{Building deployment and automation tooling:}} As a professional software developer, contributed Java and Python code to the IBM UrbanCode Deploy Blueprint Designer, including the \href{https://docs.openstack.org/heat/latest/}{OpenStack heat plugins}, and a microservice to discover cloud resources. This tool facilitated automated deployment of software and infrastructure to multiple customer environments.
\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     TECHNICAL SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{TECHNICAL SKILLS}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{center}
\begin{minipage}[b]{0.480\textwidth}
\raggedright
\begin{tightemize}
\item AWS, Azure, GCP, OCI, Vultr, OpenStack clouds \par 
\item Software Development in Python and Java \par
\item Scripting and automation (Bash, PowerShell) \par
\item Infrastructure-as-Code (IaC) \par
\item Automated VM image building (Packer) \par
\item Logging and performance monitoring \par
\item Git (GitHub, GitLab, Gerrit), SVN \par
\item Linux Administration (Red Hat, Ubuntu) \par
\item Disaster recovery planning \par
\end{tightemize}
\end{minipage}%
\begin{minipage}[b]{0.52\textwidth}
\raggedright
\begin{tightemize}
\item Terraform/OpenTofu, CloudFormation, Ansible, Chef, CDK \par
\item DevOps pipelines (GitHub Actions, GitLab CI/CD) \par
\item Networking (VPC, NSGs, NFW, WAF, Cloud WAN) \par
\item Serverless functions (including Lambda) \par
\item Basic DBA (MySQL, PostgreSQL, Oracle, Aurora) \par
\item Container development and orchestration \par
\item Docker, Podman/Buildah, Kubernetes, Fargate \par
\item S3 object storage and elastic file system\par
\item IAM permissions and security hardening \par
\end{tightemize}
\end{minipage}
\end{center}
% \sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     CERTIFICATIONS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{CERTIFICATIONS}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item \href{https://cp.certmetrics.com/amazon/en/public/verify/credential/c4ba5ed8d8c14f90996af5ee3caa6b35}{AWS Certified Cloud Practitioner} \hspace*{\fill} September 2025
\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\section{EDUCATION}
\href{http://behrend.psu.edu/}{\runsubsection{Penn State Erie, the Behrend College}}
\hspace*{\fill} \href{http://www.erie.pa.us/}{\location{Erie, Pennsylvania}}
%\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Bachelor of Software Engineering, \hspace*{\fill}June 2015 \par with minors in Management Information Systems and Computer Science
\end{tightemize}
\sectionsep

% END OF MAIN SECTION
\end{minipage}

\pagebreak
\vspace*{5em}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     PROFESSIONAL EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{PROFESSIONAL EXPERIENCE}

\runsubsection{Senior DevOps Engineer}
\descript{| Financial Technology (Credit Genie) — October 2025 - Present}
\begin{tightemize}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\item Current role - details to be added as experience develops
\end{tightemize}
\sectionsep

\vspace*{0.25em}
\runsubsection{Senior Cloud Engineer}
\descript{| Insurance Industry (Curi) — September 2021 - September 2025}
\begin{tightemize}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\item Migrated legacy servers from on-premises and VMware Cloud (VMC) to Amazon EC2 using AWS Application Migration Service.
\item Built out multiple AWS accounts with standardized networking, Service Control Policies (SCPs), and permissions boundaries using OpenTofu modules in Scalr.
\item Maintained enterprise-wide network security, including Suricata firewall rules, AWS network security groups, and NACLs.
\item Deployed and managed three Kubernetes clusters for production services, including Scalr agent pools, GitHub Actions ARC runners, and Backstage.
\item Developed Dockerfiles and implemented CI/CD pipelines to build and deploy container images to ECR, supporting ECS and Kubernetes workloads.
\item Configured CloudWatch monitoring for EC2 instances, integrating SNS notifications with Opsgenie for service downtime and low disk space alerts.
\item Automated AMI image creation for business applications and base 'golden image' templates using Hashicorp Packer.
\item Used Selenium to automate configuration and validation of commercial off-the-shelf software critical to business operations.
\end{tightemize}
\sectionsep

\vspace*{0.25em}
\runsubsection{Platform Engineer}
\descript{| Financial Services Industry (Truist) — June 2018 - September 2021}
\begin{tightemize}
\item Contributed to the development of an internal OpenStack cloud environment using VMware Integrated OpenStack.
\item Designed and maintained GitLab CI/CD pipelines for building and deploying corporate software to the OpenStack IaaS platform using Terraform.
\end{tightemize}
\sectionsep

\vspace*{0.25em}
\runsubsection{Software Engineer}
\descript{| Technology Industry (IBM) — July 2015 – June 2018}
\begin{tightemize}
\item Developed a RESTful Python-based (Flask) cloud discovery microservice for the IBM UrbanCode Deploy blueprint design server.
\item Served as a Site Reliability Engineer for the IBM Bluemix code delivery pipeline service on IBM Cloud VMs in Softlayer.
\item Created and executed scripts to manage network traffic (ingress/egress) and troubleshoot storage issues on the IBM Watson Health Life Sciences Cloud.
\end{tightemize}
\sectionsep

\end{document}  \documentclass[]{article}
